\documentclass[10pt,a4paper]{article}
\usepackage[left=12mm,right=22mm,top=10mm,bottom=5mm]{geometry}
\usepackage{eulervm}
\usepackage{amsmath,amsfonts,amsthm,amssymb}

\usepackage{tabularx}

\newcommand{\M}{\mathcal{M}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}

\pagestyle{empty}

\begin{document}
\begin{tabularx}{\textwidth}{|>{\ttfamily}X|X|} \hline
  \multicolumn{2}{|c|}{\bf ~Jean Niklas L'orange \hfill MPI Cheatsheet~~}%
  \\ \hline
  int MPI\_Allgatherv(sendbuf, sendcount, sendtype, recvbuf, recvcounts, displs,
  recvtype, comm) & Gathers data from all tasks and deliver it to all.
  \\ \hline
  int MPI\_Allgather(sendbuf, sendcount, sendtype, recvbuf, recvcount, displs,
  recvtype, comm) & Gathers data from all tasks and deliver it to all.
  \\ \hline
  int MPI\_Allreduce(sendbuf, recvbuf, count, datatype, op, comm) & Combines
  values from all processes and distribute the result back to all processes.
  \\ \hline
  int MPI\_Allgatherv(sendbuf, sendcnts, sdispls, sendtype, recvbuf, recvcnts,
  rdispls, recvtype, comm) & Sends data from all to all processes, with a
  displacement.
  \\ \hline
  int MPI\_Allgatherv(sendbuf, sendcount, sendtype, recvbuf, recvcnt,
  recvtype, comm) & Sends data from all to all processes.
  \\ \hline
  int MPI\_Bcast(buffer, count, datatype, root, comm) & Broadcasts a message
  from the process with rank {\tt root} to all other processes of the group.
  \\ \hline
  int MPI\_Gatherv(sendbuf, sendcnt, sendtype, recvbuf, recvcnts, displs,
  recvtype, root, comm) & Gathers into specified locations from all processes
  in a group.
  \\ \hline
  int MPI\_Gather(sendbuf, sendcnt, sendtype, recvbuf, recvcount, recvtype,
  root, comm) & Gathers together values from a group of processes.
  \\ \hline
  int MPI\_Recv(buf, count, datatype, source, tag, comm, status) & Basic receive.
  \\ \hline
  int MPI\_Reduce\_scatter(sendbuf, recvbuf, recvcnts, datatype, op, comm) &
  Combines values and scatters the results.
  \\ \hline
  int MPI\_Reduce(sendbuf, recvbuf, count, datatype, op, root, comm) &
  Reduces values on all processes to a single value.
  \\ \hline
  int MPI\_Scan(sendbuf, recvbuf, count, datatype, op, comm) &
  Computes the scan (partial reductions) of data on a collection of processes.
  \\ \hline
  int MPI\_Scatter(sendbuf, sendcnt, sendtype, recvbuf, recvcnt, recvtype, root,
  comm) & Sends data from one task to all other tasks in a group.
  \\ \hline
  int MPI\_Sendrecv\_replace(buf, count, datatype, dest, sendtag, source,
  recvtag, comm, status) & Sends and receives using a single buffer.
  \\ \hline
  int MPI\_Sendrecv(sendbuf, sendcount, sendtype, dest, sendtag, recvbuf,
  recvcount, recvtype, source, recvtag, comm, status) & Sends and receives a
  message.
  \\ \hline
  int MPI\_Send(buf, count, datatype, dest, tag, comm) & Performs a basic send.
  \\ \hline
\end{tabularx}
\end{document}
